\textbf{ Interpretable Gaussian Processes for Stellar Light Curves }

### 2020-08-04 tex/ms.tex
better fig
fixed figures

\begin{figure}[th!]
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/spot_expansion.pdf}
        \oscaption{spot_expansion}{%
            Polar intensity profiles for spots with different normalized
            radii $r$ in the range $(0, 1]$, computed at spherical harmonic
            degree $l_{\mathrm{max}} = 20$. Dotted black curves show profiles
            corresponding to $r < 0$ (corresponding to $r' < c_0$
            in Equation~\ref{eq:rprime}), for which the expansion does
            not converge, leading to ringing and a smaller spot contrast.
            \label{fig:spot_expansion}
        }
    \end{centering}
\end{figure}

@@

\begin{figure}[th!]
    \begin{centering}
        \includegraphics[width=0.4615\linewidth]{figures/hwhm.pdf}
        \includegraphics[width=0.475\linewidth]{figures/minr.pdf}
        \oscaption{minr}{%
            Foo bar.
            \codelink{hwhm}
            \label{fig:hwhm}
        }
    \end{centering}
\end{figure}

@@

@@

    \raisetag{15em}

@@

The final step is to evaluate the integral in Equation~(\ref{eq:Er2}), given
the PDF in Equation~(\ref{eq:lognormal}):
    \mathrm{E} \big[ y_{lm} y_{l'm'} \big]
                1 + \dfrac{\gamma_1}{1+c_0}
                \dfrac{\gamma_2}{2\gamma_1(1+c_0)}
                \dfrac{\gamma_1}{2\sqrt{2l + 1}(1+c_0)^{l+1}}
                - \dfrac{\gamma_2}{2\gamma_1(1 + c_0)} \bigg(
                \dfrac{\gamma_2}{4\sqrt{(2l + 1)(2l' + 1)}(1+c_0)^{l+l'+2}}
    \gamma_2 \equiv 1
    - 2\exp\bigg[ \mu + \frac{1}{2}\nu\bigg]
    + \exp\bigg[ 2\mu + 2\nu\bigg]
and the expression for $l' > 0, \, l = 0, \, m = m' = 0$ is again the same as in
the second case, provided we make the substitution $l \rightarrow l'$.

>>>>

\begin{figure}[p!]
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/spot_expansion.pdf}
        \oscaption{spot_expansion}{%
            Polar intensity profiles for spots with different normalized
            radii $r$ in the range $(0, 1]$, computed at spherical harmonic
            degree $l_{\mathrm{max}} = 20$. Dotted black curves show profiles
            corresponding to $r < 0$ (corresponding to $r' < c_0$
            in Equation~\ref{eq:rprime}), for which the expansion does
            not converge, leading to ringing and a smaller spot contrast.
            \label{fig:spot_expansion}
        }
    \end{centering}
\end{figure}

@@

\begin{figure}[p!]
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/hwhm.pdf}
        \oscaption{hwhm}{%
            \emph{Left.} The width $\Delta\theta$
            (Equation~\ref{eq:hwhm}) of the
            spot as a function of the radius parameter $r'$ (bottom axis)
            and the normalized radius $r$ (top axis), computed for
            $l_{\mathrm{max}} = 20$. The green dots indicate the
            minimum value of $r'$ for which the fractional error in the
            spot intensity due
            to the truncated expansion is less than one percent
            and the value of $r'$ corresponding to
            $\Delta\theta = 75^\circ$, respectively. These points correspond to
            the minimum and maximum spot sizes we consider at
            $l_{\mathrm{max}} = 20$
            (blue shading). Note that
            in this regime, the width of the spot scales approximately
            logarithmically with $r'$.
            %
            \emph{Right.} The spot width $\Delta\theta$ below which the
            fractional error in the intensity exceeds various thresholds
            as a function of maximum spherical harmonic degree
            $l_{\mathrm{max}}$. The value of $\Delta\theta$ for a tolerance
            of one percent at $l_{\mathrm{max}} = 20$ is indicated as the
            green dot for reference.
            \label{fig:hwhm}
        }
    \end{centering}
\end{figure}

@@

\vspace{1in}

@@

    \raisetag{16.5em}

@@

\clearpage

%
\noindent The final step is to evaluate the integral in Equation~(\ref{eq:Er2}), given
the PDF in Equation~(\ref{eq:lognormal}):
%
\begin{align}
    \mathrm{E} \big[ y_{lm} y_{l'm'} \big]
     & =
    \resizebox{1.4\hsize}{!}{$
            \begin{dcases}
                1 + \dfrac{\gamma_1}{1+c_0}
                \bigg[
                    -c_0 H_0^0
                    -
                    c_1 H_0^1
                    \\[0.75em]
                \qquad\qquad\enspace\enspace\quad\quad
                +
                \dfrac{\gamma_2}{2\gamma_1(1+c_0)}
                \bigg(
                \dfrac{c_0^2}{2}H_1^0
                +
                c_0 c_1 H_1^1
                +
                \dfrac{c_1^2}{2} H_1^2
                \bigg)
                \bigg]
                 &
                \qquad
                \parbox[t]{\linewidth}{\vspace{-3.5em}$l = l' = 0, \\m = m' = 0$}
                \\[2em]
                %
                %
                %
                \dfrac{\gamma_1}{2\sqrt{2l + 1}(1+c_0)^{l+1}}
                \\[0.75em]
                \enspace\quad
                \times
                \bigg[
                    c_0(2 + c_0) H_l^0 + 2 c_1(1 + c_0) H_l^1
                    + c_1^2 H_l^2
                    \\[0.75em]
                \qquad
                - \dfrac{\gamma_2}{2\gamma_1(1 + c_0)} \bigg(
                c_0^2(2 + c_0) H_{l+1}^0
                + c_0 c_1 (4 + 3 c_0) H_{l+1}^1
                \\[0.75em]
                \qquad
                + (2 + 3 c_0) c_1^2 H_{l + 1}^2
                + c_1^3 H_{l + 1}^3
                \bigg)
                \bigg]
                 &
                \qquad
                \parbox[t]{\linewidth}{\vspace{-7em}$l > 0,        \\l' = 0, \\m = m' = 0$}
                \\[2em]
                %
                %
                %
                \dfrac{\gamma_2}{4\sqrt{(2l + 1)(2l' + 1)}(1+c_0)^{l+l'+2}}
                \\[0.75em]
                \enspace\quad
                \times
                \bigg[
                    c_0^2(2+c_0)^2 H_{l + l' + 1}^0
                    + 4 c_0 (1 + c_0) (2 + c_0) c_1 H_{l + l' + 1}^1
                    \\[0.75em]
                \qquad
                + 2 \big(2 + 3 c_0 (2 + c_0)\big)c_1^2 H_{l + l' + 1}^2
                + 4(1 + c_0)c_1^3 H_{l + l' + 1}^3
                \\[0.75em]
                \qquad
                + c_1^4 H_{l + l' + 1}^4
                \bigg]
                 &
                \qquad
                \parbox[t]{\linewidth}{\vspace{-6em}$l > 0,        \\l' > 0, \\m = m' = 0$}
                \\[2em]
                %
                %
                %
                0
                 &
                \qquad m, m' \ne 0
                \quad.
            \end{dcases}
        $}
    \raisetag{16.5em}
\end{align}
%
where we define
%
\begin{align}
    \gamma_2 \equiv 1
    - 2\exp\bigg[ \mu + \frac{1}{2}\nu\bigg]
    + \exp\bigg[ 2\mu + 2\nu\bigg]
    \quad,
\end{align}
%
and the expression for $l' > 0, \, l = 0, \, m = m' = 0$ is again the same as in
the second case, provided we make the substitution $l \rightarrow l'$.
